Chapter 4

### 2021-08-06 thesis_chapter_4.Rmd
slight adjustments

# Results

## Ocean analysis

@@

ocean_vector_chp4 <- tidync("OceanParcels/chapter_4_oceanmodel/copernicus_phy001_030/global-reanalysis-phy-001-030-daily_1625758460342.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, longitude, latitude, uo, vo) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.Date(as.POSIXct(t * 3600, origin = "2019-01-01 00:00:00"),
                     "GMT",
                     "%Y-%m-%d-%h"))

ocean_summer <-  ocean_vector_chp4 %>%
  filter(t >= ("2086-01-01 00:00:00") & t <= ("2086-02-28 00:00:00"))
ocean_autumn <-  ocean_vector_chp4 %>%
  filter(t >= ("2086-03-01 00:00:00") & t <= ("2086-05-31 00:00:00"))
ocean_winter <-  ocean_vector_chp4 %>%
  filter(t >= ("2086-06-01 00:00:00") & t <= ("2086-08-30 00:00:00"))
ocean_spring <-  ocean_vector_chp4 %>%
  filter(t >= ("2086-09-01 00:00:00") & t <= ("2086-11-30 00:00:00"))

>>>>

# Results
## Ocean analysis

@@

ocean_summer <- tidync("OceanParcels/chapter_4_oceanmodel/copernicus_phy001_030/global-reanalysis-phy-001-030-daily_1625758460342.nc") %>%
  hyper_tibble() %>%
  dplyr::select(time, longitude, latitude, uo, vo) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.Date(as.POSIXct(t * 3600, origin = "2019-01-01 00:00:00"),
                     "GMT",
                     "%Y-%m-%d-%h"))
